Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-24 paper/ICPC19/icpc19.tex
fixing unicodes..

Since we want to analyze maintainability regression, we
use BCH to compute maintainability in two different versions of the Android app: a) the version of the project before the energy commit ($v_{E−1}$) and b) the version immediately after the energy commit ($v_E$). This is illustrated in Fig. [X].
Although BCH provides a detailed report of the maintainability of the project, it does not compute a final score that we can use to compare maintainability amongst different projects. Thus, based in previous work CITE?, we designed an equation to capture the distance between the current state of the project and the standard thresholds. We have adjusted the equation to meet the following requirements:

@@

where $T(l)$ is the threshold in percentage of the lines of code that are accepted to be non-compliant with the guideline for the severity level $l$. This is a standard value defined by BCH. In other words, the factor $w$ is used in Eq. \ref{eq:3} to highlight the lines of code that are not complying with the guideline. For instance, the threshold for the severity level veryHigh is defined in Table II as T(veryHigh) = 6.9\%, which derives to a weight of w(veryHigh) = 13.5. This means that, in this example, one non-compliant guideline is decreasing maintainability score by 13.5 points while a compliant guideline is increasing by 1.0 point. In addition, a version that is perfectly aligned with the standard thresholds has a maintainability score of zero. Then, we compute the difference of maintainability between the energy commit ($v_E$) and its parent commit ($v_{E−1}$), as illustrated in Fig. [X].

@@

To validate the maintainability differences in different groups of commits (e.g., baseline and energy commits) we use the Paired Wilcoxon signed-rank test with the significance level $\alpha = 0.05$. In other words, we test the null hypothesis that the maintainability difference between pairs of versions vE−1, vE (i.e., before and after an energy-commit) follows a symmetric distribution around 0. To understand the effect-size, as advocated by the Common-language effect sizes [X], we compute the mean difference, the median of the difference, and the percentage of cases that reduce maintainability.

>>>>

Since we want to analyze maintainability regression, we
use BCH to compute maintainability in two different versions of the Android app: a) the version of the project before the energy commit ($v_{E-1}$) and b) the version immediately after the energy commit ($v_E$). This is illustrated in Fig. [X].
Although BCH provides a detailed report of the maintainability of the project, it does not compute a final score that we can use to compare maintainability amongst different projects. Thus, based in previous work CITE?, we designed an equation to capture the distance between the current state of the project and the standard thresholds. We have adjusted the equation to meet the following requirements:

@@

where $T(l)$ is the threshold in percentage of the lines of code that are accepted to be non-compliant with the guideline for the severity level $l$. This is a standard value defined by BCH. In other words, the factor $w$ is used in Eq. \ref{eq:3} to highlight the lines of code that are not complying with the guideline. For instance, the threshold for the severity level veryHigh is defined in Table II as T(veryHigh) = 6.9\%, which derives to a weight of w(veryHigh) = 13.5. This means that, in this example, one non-compliant guideline is decreasing maintainability score by 13.5 points while a compliant guideline is increasing by 1.0 point. In addition, a version that is perfectly aligned with the standard thresholds has a maintainability score of zero. Then, we compute the difference of maintainability between the energy commit ($v_E$) and its parent commit ($v_{E-1}$), as illustrated in Fig. [X].

@@

To validate the maintainability differences in different groups of commits (e.g., baseline and energy commits) we use the Paired Wilcoxon signed-rank test with the significance level $\alpha = 0.05$. In other words, we test the null hypothesis that the maintainability difference between pairs of versions $v_{E-1}$, $v_E$ (i.e., before and after an energy-commit) follows a symmetric distribution around 0. To understand the effect-size, as advocated by the Common-language effect sizes [X], we compute the mean difference, the median of the difference, and the percentage of cases that reduce maintainability.
